---
title: "RDecisionTree"
author: "Rae Zhang"
date: "11/11/2021"
output:
  pdf_document: default
  word_document: default
---

# LIBRARIES

```{r}
library(rpart)   ## FOR Decision Trees
library(rattle)  ## FOR Decision Tree Vis
library(rpart.plot)
library(RColorBrewer)
library(Cairo)
library(network)
library(ggplot2)
library(ggtext)
library(readxl)
library(wordcloud)
library(RColorBrewer)
library(slam)
library(quanteda)
library(proxy)
library(stringr)
library(textmineR)
library(igraph)
library(caret)
library(ggthemes)
```

```{r}
MyPath="Crop_recommendation.csv"

RecordDF_A<-read.csv(MyPath, stringsAsFactors=TRUE)
head(RecordDF_A)
```

# Split it into a TRAINING and a TESTING set, remove the label and save it.
```{r}
str(RecordDF_A)
head(RecordDF_A)
```

## Split into TRAIN and TEST data
## Use random sampling without replacement.
```{r}
(DataSize=nrow(RecordDF_A)) 
(TrainingSet_Size<-floor(DataSize*(3/4))) ## Size for training set
(TestSet_Size <- DataSize - TrainingSet_Size) ## Size for testing set
```

## Random sample without replacement 
```{r}
set.seed(1234)
```
## The sample of row numbers
```{r}
MyTrainSample <- sample(DataSize,
                         TrainingSet_Size,replace=FALSE)

MyTrainingSET <- RecordDF_A[MyTrainSample,]
table(MyTrainingSET$label)

MyTestSET <- RecordDF_A[-MyTrainSample,]
table(MyTestSET$label)
```
## Training and Testing datasets are balanced


#  REMOVE THE LABELS from the test set
```{r}
TestKnownLabels <- MyTestSET$label
MyTestSET <- MyTestSET[ , -which(names(MyTestSET) %in% c("label"))]
```

# Decision Trees

## First - train the model with training data
## Second - test the model - get predictions - compare to the known labels.

## Create decision tree
```{r}
DT <- rpart(MyTrainingSET$label ~ ., data = MyTrainingSET, method="class")
summary(DT)
```

## Create a plot of cp
```{r}
par(bg = "#fbeed1")
par(new = F)
plotcp(DT) ## the cp plot
```

## Make another tree - change cp
```{r}
DT2<-rpart(MyTrainingSET$label ~ ., data = MyTrainingSET,cp=.049, method="class")
```

## The small cp the larger the tree if cp is too small the result will be overfitting
```{r}
summary(DT2)
```

## Third tree - here use cp = 0 and "information" as split method instead of the default which is GINI measure
```{r}
DT3<-rpart(MyTrainingSET$label ~ ., 
           data = MyTrainingSET,cp=0.02, method="class",
           parms = list(split="information"),minsplit=2)
summary(DT3)

DT3$variable.importance  ## before re-eval to add to 100
```

# Predict the Testset using all 3 trees

# Prediction 1
## Confusion Matrix and Heatmap
```{r}
(DT_Prediction= predict(DT, MyTestSET, type="class"))

confusion_matrix <- table(DT_Prediction,TestKnownLabels)
```

### Create a function that generates heatmap from the confusion matrix
```{r}
get_heatmap <- function(mapname, prediction){
  data <- as.data.frame(confusion_matrix)
  data <- as.data.frame((table(prediction,TestKnownLabels)))
plot <- ggplot(data) + 
  geom_tile(mapping=aes(x=data[,1], y=data[,2],fill=data[,3])) +
  xlab("Known Labels") +
  ylab("Decition Tress Prediction") +
  theme_economist() + 
  ggtitle(mapname) +
  scale_fill_gradient2(name="Frequency",low="#defccf", mid="#e9ffdfe6", high="#32641b") +
  theme(plot.background = element_rect(fill='#fbeed1',color="#fbeed1"),
        legend.background =element_rect(fill='#fbeed1',color="#fbeed1"),
        axis.text.x = element_markdown(size=12, angle = 30, vjust = 0.9, hjust=.6),
        axis.text.y = element_markdown(size=12, angle = 0, vjust = 0.2, hjust=1.1))
return(plot)
}
```
## Use the function to generate a confusion matrix heatmap of decision tree 1's prediction
```{r}
get_heatmap('Confusion Matrix Heatmap of prediction 1', DT_Prediction)
```


# Visualizations
## Decision Tree 1
```{r}
par(new = F)
fancyRpartPlot(DT, main="Decision Tree CP=default Type=Class Split=default", cex=0.3)
```


# Prediction 2 
## Confusion Matrix and Heatmap
```{r}
(DT_Prediction2= predict(DT2, MyTestSET, type = "class"))
confusion_matrix <- table(DT_Prediction2, TestKnownLabels)
get_heatmap('Confusion Matrix Heatmap of prediction 2', DT_Prediction2)
```

# Visualizations
# Decision Tree 2
```{r}
par(new = F)
fancyRpartPlot(DT2, cex=.9, main="Decision Tree CP=0.049 Type=Class Split=default")
```


# Prediction 3
## Confusion Matrix and Heatmap
```{r}
(DT_Prediction3= predict(DT3, MyTestSET, type = "class"))
confusion_matrix <- table(DT_Prediction3, TestKnownLabels)
get_heatmap('Confusion Matrix Heatmap of prediction 3', DT_Prediction3)
```

# Visualizations
# Decision Tree 3
```{r}
par(new = F)
rattle::fancyRpartPlot(DT3,main="Decision Tree CP=0.02 Type=Class Split=information", cex=.4)
```

